%-------------------------
% Resume in Latex
% Author : Wojciech Michaluk
% Based off: https://github.com/aderylo/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.08003pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  {\Huge \scshape Wojciech Michaluk} \\[5pt] % Adds spacing below the name
  \small
  \faPhone\ +48 500 424 248 ~ 
  \href{mailto:wojo.michaluk@gmail.com}{\faEnvelope\ wojo.michaluk@gmail.com} ~
  \href{https://www.linkedin.com/in/wojciech-michaluk-a09465269/}{\faLinkedin\ wojciech-michaluk} ~
  \href{https://github.com/wojo501}{\faGithub\ github.com/wojo501} \\[3pt]
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

% WUT - all accolades
\resumeSubheading
{Warsaw University of Technology}{Oct. 2021 -- Feb. 2025 (Expected)}
{BSc of Data Science}{Warsaw, Poland}
\resumeItemListStart
\resumeItem{Best technical univeisty in Poland according to the Perspektywy ranking.}
\resumeItemListEnd

% TU - all accolades
\resumeSubheading
{Vienna University of Technology}{Mar. 2024 -- Sept. 2024}
{MSc of Data Science (Scholarship)}{Vienna, Austria}
\resumeItemListStart
\resumeItem{Best technical univeisty in Austria according to the QS ranking.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Programming Languages}{: Python, Java, Kotlin, R, Typescript, Matlab} \\
                \textbf{Technologies}{: SQL, AWS, Spark, Hive, NiFi, MongoDB, Git} \\
                \textbf{Natural languages}{: English (C1 - IELTS), Polish (Native), German (A2 - Certificate University of Vienna)} \\
                \textbf{Driving license}{: AM, A2, B2, Yachts, Motorboats}\\
          }}
\end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% Amazon
\resumeSubheading
{Amazon}{Jul. 2024 - Oct. 2024}
{Software Engineering Intern $|$ Amazon Web Services, Kotlin, TypeScript, Git}{Madrid, Spain}
\resumeItemListStart
\resumeItem{Mobile development for iOS and Android for Amazon Devices division}
\resumeItem{Developed a Business Metrics controlling system in \href{https://play.google.com/store/apps/details?id=com.amazon.tahoe.grownups&hl=en}{Kids+ Parent Dashboard} mobile app (100K+ downloads in Google Store)}
\resumeItem{Implemented infrastructure using 5+ Amazon Web Services: Cognito, Kinesis, Lambda, S3, Pipelines ect.}
\resumeItem{Established end-to-end testing with JUnit.}
\resumeItemListEnd

% Essembli - all
\resumeSubheading
{Essembli}{Oct. 2023 - Jan. 2024}
{Junior Java Developer $|$ SQL, Java, Mercurial}{Warsaw, Poland}
\resumeItemListStart
\resumeItem{Oracle Customer Care and Billing service maintenance for 3 foreign customers.}
\resumeItem{Code developemnet with Java and data analysis with SQL.}
\resumeItem{Member of 10 developers team. Staying in touch with analysts, working in scrum.}
\resumeItemListEnd

% Infosys - all
\resumeSubheading
{Infosys}{Jul. 2023 - Sept. 2023}
{Full Stack/AI Intern $|$ Python (HuggingFace, Flask), Java, Swagger, Git}{Bangalore, India}
\resumeItemListStart
\resumeItem{Created dataset for Large Language Model finetuning in Python with 80K+ data rows.}
\resumeItem{Swagger API design, API implementation in Spring Boot.}
\resumeItem{The distinguished hackathon project among 20 teams.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\vspace{5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://github.com/matkubita/ClickbaitDetectionThesis}{\textbf{Clickbait News Detection and Analysis} (Thesis Link)} $|$ \emph{Python, Pytorch, JavaScript, LaTeX}}{Jul. 2024 - Feb. 2025}
\resumeItemListStart
\resumeItem{Bachelor's thesis at Warsaw University of Technology. Developed a browser extension for clickbait detection and analysis using NLP modules.}
\resumeItem{Collaborated internationally with professors from Modul University Vienna.}
\resumeItem{Achieved 82\% accuracy in clickbait detection using machine learning models based on large language model embeddings.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Machine Learning \& Deep Neural Networks} $|$ \emph{Python, Pytorch}}{Oct. 2022 - Jul. 2024}
\resumeItemListStart
\resumeItem{\href{https://github.com/wojo501/speml24_2}{Centralised and Federated Learning for image classification (Link).}}
\resumeItem{\href{https://github.com/wojo501/recommender_systems}{Recommender Systems Challenge \textit{WeKnowWhatYouWant} (Link).}}
\resumeItem{\href{https://github.com/wojo501/dlvc_2}{Deep Learning in Visual Computing (Link).}}
\resumeItem{\href{https://github.com/wojo501/mtt-distillation-neural-networks}{Implementation of ML paper: \textit{Dataset Distillation by Matching Training Trajectories} (Link).}}
\resumeItem{\href{https://github.com/wojo501/clustering-ML}{Clustering methods (Link).}}
\resumeItem{\href{https://github.com/wojo501/binary-classification-practice-ML}{Kaggle Binary Classification Challange (Link).}}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Data Processing \& Visualization} $|$ \emph{R, Shiny, Java, Spark, AWS, JavaScript}}{Oct. 2021 - Jul. 2024}
\resumeItemListStart
\resumeItem{\href{https://github.com/wojo501/data_intensive_computing_task_2}{Data Intensive Computing with Spark and AWS (Link).}}
\resumeItem{\href{https://github.com/wojo501/todos-react-final-project}{ToDos React Web App (Link).}}
\resumeItem{\href{https://github.com/wojo501/TWD-google-maps-dashboard}{Google Maps Dashboard Data Visualization (Link).}}
\resumeItem{\href{https://github.com/wojo501/crypto-dashboard-final-project}{Crypto Currencies Tracker Dashboard (Link).}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------VOLUNTEERING AND ORGANISATIONS-----------
\section{Volunteering \& Organisations}
\vspace{5pt}
\resumeSubHeadingListStart

% Sailing instructor - all
\resumeSubheading
{Sailing Instructor}{Jun. 2021 - Sep. 2021}
{Skipper}{Ryn, Poland}
\resumeItemListStart
\resumeItem{Maintained safety and boating credentials. Planning daily class performance according to the weather.
}
\resumeItemListEnd

% Math/Physics tutor - all
\resumeSubheading
{Math and Physics Tutor}{Sep. 2019 - Jun. 2023}
{On my own}{Gdansk, Poland}
\resumeItemListStart
\resumeItem{Support students with final high-school exam preparation for 4 years.}
\resumeItemListEnd

% Alpenverein - all
\resumeSubheading
{Alpenverein Volunteer}{2018 - 2021}
{Alpenverein}{Wachau, Austria}
\resumeItemListStart
\resumeItem{Supported endangered species protection initiatives in Austria.}
\resumeItem{Effectively communicated with an international team of
volunteers, utilizing strong interpersonal skills}
\resumeItemListEnd

% Math/Physics tutor - all
\resumeSubheading
{Science Community \textit{Talented from Pomerania}}{2018 - 2021}
{Talented from Pomerania}{Pruszcz Gdanski, Poland}
\resumeItemListStart
\resumeItem{Engaged in a Science Program uniting talented students from Pomerania, Poland, expanding my expertise in Physics.}
\resumeItem{Attending lectures at Gdansk University of Technology.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------Extracurricular------------
\section{Extracurricular}
\begin{itemize}[leftmargin=0.35in]
  \small{\item{\textit{Machine Learning in Engineering Applications} ATHENS programme at Istambul University of Technology}}
  \vspace{-7pt}
  \small{\item{Hackaton \textit{Climathon 2023} in Katowice}}
  \vspace{-7pt}
\end{itemize}
\vspace{-16pt}

\end{document}
